\bf Visualising How Non-linear Dimension Reduction Warps Your Data

### 2024-01-12 paper.qmd
Change the wording 31th to 31st, rescaled with coord_cartesian

p1 <-  ggplot(data = hex_full_count_df_loop1, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_point(data = UMAP_data, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(-5, 7) +
  ylim(-10, 10) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "a", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

@@

p2 <-  ggplot(data = hex_full_count_df_loop2, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_point(data = UMAP_data, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  xlim(-5, 8) +
  ylim(-10, 10) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "b", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

@@

p3 <-  ggplot(data = hex_full_count_df_loop3, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_point(data = UMAP_data, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "c", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

@@

```{r}
#| warning: false
#| echo: false
#| label: fig-wkhighD
#| fig-cap: How the 2D model lift into high dimensions? (a) visualize the points and the hexagonal bin centroids related 31th and 239th hexagons, (b) visualization of the edge connected the 31th and 239th hexagons (colored in red) in the triangular mesh. A video of tour animation is available at (need to add the link of lg_high).

>>>>

p1 <-  ggplot(data = hex_full_count_df_loop1, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_point(data = UMAP_data, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  coord_cartesian(xlim =c(-5, 7), ylim = c(-10, 10)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "a", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

@@

p2 <-  ggplot(data = hex_full_count_df_loop2, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_point(data = UMAP_data, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  coord_cartesian(xlim =c(-5, 7), ylim = c(-10, 10)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "b", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

@@

p3 <-  ggplot(data = hex_full_count_df_loop3, aes(x = x, y = y)) +
  geom_polygon(color = "black", aes(group = polygon_id, fill = std_counts)) +
  geom_point(data = UMAP_data, aes(x = UMAP1, y = UMAP2), alpha = 0.5) +
  scale_fill_viridis_c(direction = -1, na.value = "#ffffff", option = "C") +
  coord_cartesian(xlim =c(-5, 7), ylim = c(-10, 10)) +
  theme_void() +
  theme(legend.position="none", legend.direction="horizontal", plot.title = element_text(size = 7, hjust = 0.5, vjust = -0.5),
        axis.title.x = element_blank(), axis.title.y = element_blank(),
        axis.text.x = element_blank(), axis.ticks.x = element_blank(),
        axis.text.y = element_blank(), axis.ticks.y = element_blank(),
        panel.grid.major = element_blank(), panel.grid.minor = element_blank(), #change legend key width
        legend.title = element_text(size=8), #change legend title font size
        legend.text = element_text(size=6)) +
  guides(fill = guide_colourbar(title = "Standardized count")) +
  annotate(geom = 'text', label = "c", x = -Inf, y = Inf, hjust = -0.3, vjust = 1, size = 3)

@@

```{r}
#| warning: false
#| echo: false
#| label: fig-wkhighD
#| fig-cap: How the 2D model lift into high dimensions? (a) visualize the points and the hexagonal bin centroids related 31st and 239th hexagons, (b) visualization of the edge connected the 31th and 239th hexagons (colored in red) in the triangular mesh. A video of tour animation is available at (need to add the link of lg_high).

### 2024-01-12 paper.tex
Change the wording 31th to 31st, rescaled with coord_cartesian

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, sharp corners, frame hidden, interior hidden, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, breakable]}{\end{tcolorbox}}\fi

@@

\caption{\label{fig-wkhighD}How the 2D model lift into high dimensions?
(a) visualize the points and the hexagonal bin centroids related 31th
and 239th hexagons, (b) visualization of the edge connected the 31th and
239th hexagons (colored in red) in the triangular mesh. A video of tour
animation is available at (need to add the link of lg\_high).}

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, breakable, frame hidden, sharp corners]}{\end{tcolorbox}}\fi

@@

\caption{\label{fig-wkhighD}How the 2D model lift into high dimensions?
(a) visualize the points and the hexagonal bin centroids related 31st
and 239th hexagons, (b) visualization of the edge connected the 31th and
239th hexagons (colored in red) in the triangular mesh. A video of tour
animation is available at (need to add the link of lg\_high).}
